\chapter{Introduction}

LEDs are exceptionally efficient when compared to legacy lighting technologies like arc, incandescent, fluorescent lighting, and others. The advantages inherent to the technology have allowed LEDs to enter a variety of light applications like automotive, general lighting, and display backlighting and many other use-cases. \cite{uLED_review}
Conventional inorganic LEDs have MESA dimensions generally greater than $(300\times 300) \umm$, however \uleds \ target an area below $(100\times 100) \umm$ to $1 \umm$ \cite{parbrook2021micro}

One of the earliest claims to the discoveries of the LED was by Oleg Losev in the 1920s, the work was generally ignored and the conjectured theory for the operation was incorrect, the subsequent research also focused on $\ch{SiC}$ and \rom{2}-\rom{4} semiconductors. This era of research was generally impractical and did not produce sufficient light. However, with the arrival of \rom{3}-\rom{5} semiconductors like $\ch{GaAs}$, $\ch{GaSb}$, $\ch{InP}$, and $\ch{SiGe}$ there was significant progress in luminosity, although sadly this was all within the infrared spectrum.
Visible LEDs would emerge as research in the area quickened, the technology was based on $\ch{GaAsP}$ epitaxy over $\ch{GaAs}$ substrates. This would bring forth the advent of commercializable LEDs that would now be seen everywhere. Eventually efficiency and luminosity would surpass that of traditional lighting solutions like filament based tungsten and bring us to where we are today with LEDs being used in nearly all lighting and display applications.




\section{Motivation for \uleds \ as a Technology}
LCDs and OLEDs currently dominate the display market, each technology comes with its trade-offs and current innovations with quantum dots and fully addressable back-lit mini-LED panels aim to address some shortcomings concerning contrast, colour accuracy, power consumption, brightness, lifetime, and response times.

\uleds \ aim to address many of these concerns as well, by offering a number of advantages over traditional LCD and OLED displays. The biggest advantage \uled s would provide over LCDs is the power efficiency where LCDs suffer from high power loss due to the multiple diffuser and filtering layers required to compose a screen \cite{LCD_bad}. A commonly cited number is that LCDs loose nearly 70-90\% of the flux introduced by the backlight to the various polarizing layers that comprise the display. In contrast, as \uled  displays would be entirely emissive, none of the light would be lost to the conventional filtering layers.
% (IS THIS EVEN TRUE, IS LIGHT LOST TO PHOSPHOR LAYERS?)


% \section{Hurdles in \uled \ Technology}

There are a variety of hurdles \uled  \ technology, many of which arise from the high production cost and the low external quantum efficiency of the technology \cite{uledhurdles}. As such adoption has been infeasible as yet.
% IDENTIFY COMMON HURDLES IN MICRO LED TECHNOLOGY

% SHOW WHICH OF THESE PROBLEMS WE ARE AIMING TO FIX OR SOLVE FOR


% \section{Motivation for Indium as a Diebonding Material}

As we are attempting to use indium as a diebonding material, there is adequate justification for such use. Indium diebonding comes with a variety of advantages, the first and foremost being that it is a very forgiving material in a wide variety of ways \cite{indiumCorpBath}. Indium electroplating can be done at room temperature, the material has a useful low melting point of $\approx 150 \dC$ \cite{indiumCorpConstants} and is also an incredibly soft and ductile material. Lastly it also is very resistant to forming thick surface oxides and easily wets to surfaces when it reaches its melting temperature \cite{indium_diebonding}.

Due to the many advantages of the material it is an easy choice to begin with to minimize constraints on other portions of the project.

% EASE OF INDIUM AS AN ELECTROPLATING MATERIAL

% LOW MELTING POINT

% SOFTNESS OF MATERIAL/DUCTILITY

% LOW likelihood OF SURFACE OXIDES

% EASE OF WETTING TO SURFACE
